Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-04-07 paper/01-introduction.tex
done w/ writting

One negative side effect of name-based requests is that any on-path or
eavesdropping adversary between a consumer and producer can learn the identity
and contents of all data in transit. In traditional IP-based networks, there are
generally two types of mechanisms to solve this problem: (1) anonymity
networks such as Tor \cite{tor} or (2) VPNs. As tools focused on anonymity,
the former help prevent linkability of packets to their requestors without
always protecting the identities or content themselves. In contrast, VPNs focus
on packet confidentiality by creating a tunnel between two private networks
or a consumer and single private network. All traffic over this tunnel is
encrypted and thereby opaque to an eavesdropper. VPNs differ from anonymity
networks such as Tor in that they are \emph{network-layer} mechanisms that
typically only introduces a single layer of encryption to protect traffic.
Thus, while Tor can be used to enable VPN-like functionality, it is often
far more inefficient since it operates above the network layer.

>>>>

One negative side effect of name-based requests is that any on-path or
eavesdropping adversary between a consumer and producer can learn the identity
and contents of all data in transit. In traditional IP-based networks, there are
generally two types of mechanisms to solve this problem: (1) anonymity
networks such as Tor \cite{dingledine2004tor} or (2) VPNs. As tools focused on anonymity,
the former help prevent linkability of packets to their requestors without
always protecting the identities or content themselves. In contrast, VPNs focus
on packet confidentiality by creating a tunnel between two private networks
or a consumer and single private network. All traffic over this tunnel is
encrypted and thereby opaque to an eavesdropper. VPNs differ from anonymity
networks such as Tor in that they are \emph{network-layer} mechanisms that
typically only introduces a single layer of encryption to protect traffic.
Thus, while Tor can be used to enable VPN-like functionality, it is often
far more inefficient since it operates above the network layer.

### 2017-04-07 paper/05-sec-analysis.tex
done w/ writting

\textbf{Denial of Service:} Since CCVPN gateways are connected to the public network they are clearly susceptible to DoS attacks. In the CCVPN architecture, both $G_c$ and $G_p$ are susceptible to DoS attacks. A DoS attack on $G_p$ would consist in flooding it with several fake encapsulated interests. Conversely, a DoS attack on $G_c$ would basically consist of flooding it with an enormous amount of encrypted content packets. In the case of $G_p$, such attacks are specially harmful since the interest decapsulation involves a public-key decryption operation.

@@

\textit{\textbf{Proof--}} This follows directly from the definition of CCA security and the
argument in the above proof.

>>>>

\textbf{Denial of Service:} Since CCVPN gateways are connected to the public network they are clearly susceptible to DoS attacks. In the CCVPN architecture, both $G_c$ and $G_p$ are susceptible to DoS attacks. A DoS attack on $G_p$ would consist in flooding it with several fake encapsulated interests. Conversely, a DoS attack on $G_c$ would basically consist of flooding it with an enormous amount of encrypted content packets. In the case of $G_p$, such attacks are specially harmful since the interest decapsulation involves a public-key decryption operation. We plan to consider DoS countermeasures in future work.

@@

\textit{\textbf{Proof--}} This follows directly from the definition of CCA-security and from the
same argument in the previous proof.

### 2017-04-07 paper/07-experiment.tex
done w/ writting

\begin{figure}[]
\centering
\includegraphics[width=\columnwidth]{images/testnet.eps}
\caption{Testbed network topology. $M$ consumers and $N$ producers}\label{testnet}
\end{figure}

\begin{figure}[]
\centering
\includegraphics[width=\columnwidth]{images/times.pdf}
\caption{Execution time of the algorithms in CCVPN design}\label{times}
\end{figure}

\begin{figure}[]
\centering
  \subfigure[Throughput]{\includegraphics[width=0.8\columnwidth]{images/1_1_thput.pdf}\label{1a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.8\columnwidth]{images/1_1_rtt.pdf}\label{1b}}
\caption{CCVPN performance with one consumer and one producer for increasing interest issuance rates.}\label{exp1}
\end{figure}

\begin{figure}[]
\centering
  \subfigure[Throughput]{\includegraphics[width=0.8\columnwidth]{images/n_1_thput.pdf}\label{2a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.8\columnwidth]{images/n_1_rtt.pdf}\label{2b}}
\caption{CCVPN performance with multiple consumers and one producer. Each consumer requests with 1 mbps rate.}\label{exp2}
\end{figure}

\begin{figure}[]
\centering
  \subfigure[Throughput]{\includegraphics[width=0.8\columnwidth]{images/n_n_thput.pdf}\label{3a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.8\columnwidth]{images/n_n_rtt.pdf}\label{3b}}
\caption{CCVPN performance with multiple consumers and multiple producers. Each consumer requests with 1 mbps rate.}\label{exp3}
\end{figure}

@@

\todo{TODO}

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/testnet.eps}
\caption{Testbed network topology. $M$ consumers and $N$ producers}\label{testnet}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/times.pdf}
\caption{Execution time of the algorithms in CCVPN design}\label{times}
\end{figure}

\begin{figure}
\centering
  \subfigure[Throughput]{\includegraphics[width=0.8\columnwidth]{images/1_1_thput.pdf}\label{1a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.8\columnwidth]{images/1_1_rtt.pdf}\label{1b}}
\caption{CCVPN performance with one consumer and one producer for increasing interest issuance rates.}\label{exp1}
\end{figure}

\begin{figure}
\centering
  \subfigure[Throughput]{\includegraphics[width=0.7\columnwidth]{images/n_1_thput.pdf}\label{2a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.7\columnwidth]{images/n_1_rtt.pdf}\label{2b}}
\caption{CCVPN performance with multiple consumers and one producer. Each consumer requests with 1 mbps rate.}\label{exp2}
\end{figure}

\begin{figure}
\centering
  \subfigure[Throughput]{\includegraphics[width=0.7\columnwidth]{images/n_n_thput.pdf}\label{3a}}
  \hfil
  \subfigure[Avg. RTT]{\includegraphics[width=0.7\columnwidth]{images/n_n_rtt.pdf}\label{3b}}
\caption{CCVPN performance with multiple consumers and multiple producers. Each consumer requests with 1 mbps rate.}\label{exp3}
\end{figure}

@@

CCVPN  exhibits moderately good results with respect to the network load capacity, considering the overheads implied by the deployment of secure tunnels over the CCN architecture.
With gateways' processes running each on a single core of a single processor, the VPN was capable of providing reasonable throughput to up to 70 clients.
This performance results are a lower bound that can be improved in several ways, among which we highlight:

\begin{enumerate}
 \item \textbf{Implementation optimization:} The CCNx software stack is an ongoing research project, and as such, the implementation focus on functionality rather than performance.
 We believe that the results presented in this section could be significantly improved by optimizations that do not rely exclusively on CCVPN design, but also in CCNx software.
 \item \textbf{Distributed and parallel processing:} In a real deployment scenario, we expect that a large scale organization, which wants to implement a VPN service, to have dedicated network devices running
 the gateway service, possibly in multiple cores. Moreover, it is not hard to imagine multiple VPN gateways sharing the load in a large organization.
 In such scenarios, we expect the network capacity (in terms throughput or number of simultaneous consumers) to scale linearly with the increase of dedicated computational resources.
 \item \textbf{Caching:} Content caching is a major advantage of ICNs when compared to the IP model. In our experiments we wanted to evaluate the worst case scenario. Therefore, clients always request different contents
 and content caching does not happen. In a real world deployment, contents that are popular (inside the VPN) would be potentially cached, significantly increasing the throughput and reducing the RTT.

\end{enumerate}

### 2017-04-07 paper/ccvpn.tex
experiments section done, missing discussion
done w/ writting

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

\usepackage{microtype}

@@

\usepackage{algorithm2e}
%\usepackage{algorithm,algorithmic}
\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}

@@

\section{Conclusion}\label{sec:conclusion}
We presented the design, implementation, and assessment of CCVPN, a scheme and
protocol for building secure and private tunnels in CCN. CCPN allows two namespaces
to be bridged by a tunnel across a public network. Unlike point-to-point tunnels,
such as those enabled by secure session protocols, CCVPN allows many consumers
to share the tunnel to access the private namespace. CCVPN is designed with efficiency
in mind: public-key cryptographic operations are kept to a minimum during normal
operation; symmetric-key packet encapsulation algorithms are used to marshall
packets between gateways. Our experimental evidence indicate that CCVPN offers
modest performance in the presence of a variable number of consumers and producers.
The results suggest that CCVPN could be deployed for private namespace tunneling
in real world CCN deployments.

For future work, we plan to implement the CCNxKE protocol from \ref{ccnxke} as a
way to bootstrap symmetric-key tunnels in CCVPN. We will also integrate CCVPN into
real world testbeds to assess its performance for real-world applications. These
include video streaming and large-scale content dissemination applications.

>>>>

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% 
\usepackage{microtype}

@@

\usepackage{algorithm2e}
\usepackage{algorithm,algorithmic}
\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}

@@

\section{Conclusion}\label{sec:conclusion}
We presented the design, implementation, and assessment of CCVPN, a scheme and
protocol for building secure and private tunnels in CCN. CCVPN allows two namespaces
to be bridged by a tunnel across a public network. Unlike point-to-point tunnels,
such as those enabled by secure session protocols, CCVPN allows many consumers
to share the tunnel to access the private namespace. CCVPN is designed with efficiency
in mind: public-key cryptographic operations are kept to a minimum during normal
operation; symmetric-key packet encapsulation algorithms are used to marshall
packets between gateways. Our experimental evidence indicate that CCVPN offers
modest performance in the presence of a variable number of consumers and producers.
The results suggest that CCVPN could be deployed for private namespace tunneling
in real world CCN deployments.

For future work, we plan to implement the CCNxKE protocol from~\cite{ccnxke} as a
way to bootstrap symmetric-key tunnels in CCVPN. We will also integrate CCVPN into
real world testbeds to assess its performance for real-world applications. These
include video streaming and large-scale content dissemination applications. Finally,
we plan to investigate countermeasures to DoS attacks on CCVPN, such as puzzles for tunnel establishment.
